Demo arXiv template

### 2022-10-05 paper/paper.qmd
update on abstract and intro

---
title: "Demo arXiv template"
format:
  arxiv-pdf:
    keep-tex: true  
  arxiv-html: default
author:
  - name: H. Sherry Zhang
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: 29 Ancora Imparo Way, Clayton
        city: Melbourne, VIC
        country: Australia
    orcid: 0000-0002-7122-1463
    email: huize.zhang@monash.edu
    url: https://huizezhangsh.netlify.app/
  - name: Collaborators
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: 29 Ancora Imparo Way, Clayton
        city: Melbourne, VIC
        country: Australia
abstract: |
  - Indices, useful, quantify severity, early monitoring, 
  - A huge number of indices have been proposed by domain experts, however, a large majority of them are not being adopted and reused in research or in practice. 
  - One of the most commonly used drought index, SPI and SPEI, are available through the `SPEI` package and its readily avaiability to be applied on user's data 
  - However, even if most of the indices have available existing implementation available to users, there would be hundreds of them and it will be burdensome to remember
  - The paper describes a general pipeline framework to construct indices from spatio-temporal data, so that indices can be constructed through [a set of general steps].
  - The benefit of such a framework is that ...
  - The framework will be demonstrated with drought indices as examples, but appliable in general to environmental indices constructed from multivariate spatio-temporal data
keywords: 
  - spatio-temporal data
  - indices
  - data pipeline
bibliography: bibliography.bib  
---

@@

Various methods are proposed to extract multivariate information on the spatial coverage, across time.

Indices with readily available code to implement have more potential to be computed by researchers, i.e. the package `SPEI` [@SPEI] has implemented the SPI and SPEI index for calculating drought indices. [Another package in a different domain]

Each individual index follows its own data pipeline and it can be difficult to evaluate how an index can be affected by tweaking parameters in a certain step, rearranging the order of steps, using to different method. 
This paper proposes a data pipeline for constructing indices using multivariate spatio-temporal data.
The steps involved in the pipeline are general in nature and flexible to be adopted to most index construction for environmental data.

>>>>

---
title: "Demo arXiv template"
format:
  arxiv-pdf:
    keep-tex: true  
  arxiv-html: default
author:
  - name: H. Sherry Zhang
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: 29 Ancora Imparo Way, Clayton
        city: Melbourne, VIC
        country: Australia
    orcid: 0000-0002-7122-1463
    email: huize.zhang@monash.edu
    url: https://huizezhangsh.netlify.app/
  - name: Collaborators
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: 29 Ancora Imparo Way, Clayton
        city: Melbourne, VIC
        country: Australia
abstract: |
  - Indices, useful, quantify severity, early monitoring, 
  - A huge number of indices have been proposed by domain experts, however, a large majority of them are not being adopted, reused, and compared in research or in practice. 
  - One of the reasons for this is the plenty of indices are quite complex and there is no obvious easy-to-use implementation to apply them to user's data. 
  - The paper describes a general pipeline framework to construct indices from spatio-temporal data, 
  - This allows all the indices to be constructed through a uniform data pipeline and different indices to vary on the details of each step in the data pipeline and their orders. 
  - The pipeline proposed aim to smooth the workflow of index construction through breaking down the complicated steps proposed by various indices into small building blocks shared by most of the indices.
  - The framework will be demonstrated with drought indices as examples, but appliable in general to environmental indices constructed from multivariate spatio-temporal data
keywords: 
  - spatio-temporal data
  - indices
  - data pipeline
bibliography: bibliography.bib  
---

@@

Various methods are proposed to extract multivariate information on the spatial coverage, across time.
Each individual index follows its own data pipeline and it can be difficult to evaluate how an index can be affected by tweaking parameters in a certain step, rearranging the order of steps, using to different method.

Indices with readily available code to implement have more potential to be computed by researchers, i.e. the package `SPEI` [@SPEI] has implemented the SPI and SPEI index for calculating drought indices. 
[Another package in a different domain].  
However, even if most of the indices have available existing implementation available to users, there would be hundreds of them and it will be burdensome to remember, classify, and compare between.
There is a need for a framework to generally describe how indices can be constructed from spatio-temporal data.

This paper proposes such data pipeline for constructing indices.
The steps involved in the pipeline are general in nature and flexible to be adopted to most index construction for environmental data.

### 2022-10-05 paper/paper.tex
update on abstract and intro

\title{Demo arXiv template}
\author{
\textbf{H. Sherry Zhang}~\orcidlink{0000-0002-7122-1463}\\Department of
Econometrics and Business Statistics\\Monash University\\Melbourne,
VIC\\\href{mailto:huize.zhang@monash.edu}{huize.zhang@monash.edu}\\\\\\
\textbf{Collaborators}\\Department of Econometrics and Business
Statistics\\Monash University\\Melbourne, VIC\\}
\date{}
\begin{document}
\maketitle
\begin{abstract}
\begin{itemize}
\tightlist
\item
  Indices, useful, quantify severity, early monitoring,
\item
  A huge number of indices have been proposed by domain experts,
  however, a large majority of them are not being adopted and reused in
  research or in practice.
\item
  One of the most commonly used drought index, SPI and SPEI, are
  available through the \texttt{SPEI} package and its readily
  avaiability to be applied on user's data
\item
  However, even if most of the indices have available existing
  implementation available to users, there would be hundreds of them and
  it will be burdensome to remember
\item
  The paper describes a general pipeline framework to construct indices
  from spatio-temporal data, so that indices can be constructed through
  {[}a set of general steps{]}.
\item
  The benefit of such a framework is that \ldots{}
\item
  The framework will be demonstrated with drought indices as examples,
  but appliable in general to environmental indices constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
{\bfseries \emph Keywords}
\def\sep{\textbullet\ }
spatio-temporal data \sep indices \sep 
data pipeline

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners, frame hidden, interior hidden]}{\end{tcolorbox}}\fi

@@

Various methods are proposed to extract multivariate information on the
spatial coverage, across time.

Indices with readily available code to implement have more potential to
be computed by researchers, i.e.~the package \texttt{SPEI} (Beguería and
Vicente-Serrano 2017) has implemented the SPI and SPEI index for
calculating drought indices. {[}Another package in a different domain{]}

Each individual index follows its own data pipeline and it can be
difficult to evaluate how an index can be affected by tweaking
parameters in a certain step, rearranging the order of steps, using to
different method. This paper proposes a data pipeline for constructing
indices using multivariate spatio-temporal data. The steps involved in
the pipeline are general in nature and flexible to be adopted to most
index construction for environmental data.

>>>>

\title{Demo arXiv template}
\author{
\textbf{H. Sherry Zhang}~\orcidlink{0000-0002-7122-1463}\\Department of
Econometrics and Business Statistics\\Monash University\\Melbourne,
VIC\\\href{mailto:huize.zhang@monash.edu}{huize.zhang@monash.edu}\\\\\\
\textbf{Collaborators}\\Department of Econometrics and Business
Statistics\\Monash University\\Melbourne, VIC\\}
\date{}
\begin{document}
\maketitle
\begin{abstract}
\begin{itemize}
\tightlist
\item
  Indices, useful, quantify severity, early monitoring,
\item
  A huge number of indices have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indices are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indices
  from spatio-temporal data,
\item
  This allows all the indices to be constructed through a uniform data
  pipeline and different indices to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indices into small building blocks shared by most of the indices.
\item
  The framework will be demonstrated with drought indices as examples,
  but appliable in general to environmental indices constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
{\bfseries \emph Keywords}
\def\sep{\textbullet\ }
spatio-temporal data \sep indices \sep 
data pipeline

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

Various methods are proposed to extract multivariate information on the
spatial coverage, across time. Each individual index follows its own
data pipeline and it can be difficult to evaluate how an index can be
affected by tweaking parameters in a certain step, rearranging the order
of steps, using to different method.

Indices with readily available code to implement have more potential to
be computed by researchers, i.e.~the package \texttt{SPEI} (Beguería and
Vicente-Serrano 2017) has implemented the SPI and SPEI index for
calculating drought indices. {[}Another package in a different
domain{]}.\\
However, even if most of the indices have available existing
implementation available to users, there would be hundreds of them and
it will be burdensome to remember, classify, and compare between. There
is a need for a framework to generally describe how indices can be
constructed from spatio-temporal data.

This paper proposes such data pipeline for constructing indices. The
steps involved in the pipeline are general in nature and flexible to be
adopted to most index construction for environmental data.
